Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-15 MUSES_vs_BYOD_solutions.tex
Justificación del uso del servidor
En el paper y en las respuestas a los revisores

\author{P. de las Cuevas, A.M. Mora, J.J. Merelo}
\ead{\{paloma, amorag, jmerelo\}@geneura.ugr.es}
\address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
%\author{A. M. Mora}
%\ead{amorag@geneura.ugr.es}
%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}

@@

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} program will be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side would be installed in the corporate SOC. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the information flows labelled as 'Info XX'. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras

@@

The rationale for this approach is based on two main reasons: 1) there is a need for a high computational power in order to perform the event correlation and self-adaptation processes, so a quite powerful machine should be used (server); 2) there are two clearly separated parts in the system, namely the users (client) and the enterprise (server).

@@

All data in MUSES will be encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.

>>>>

\author{P. de las Cuevas, A.M. Mora, J.J. Merelo, P. García-Sánchez, A. Fernández-Ares}
\ead{\{paloma, amorag, jmerelo, pgarcia, antares\}@geneura.ugr.es}
\address{Departamento de Arquitectura y Tecnología de Computadores.\\ ETSIIT - CITIC. University of Granada, Spain}
%\author{A. M. Mora}
%\ead{amorag@geneura.ugr.es}
%\address{Departamento de Arquitectura y Tecnología de Computadores. Escuela Técnica Superior de Ingenierías Informática y de Telecomunicación. CITIC. University of Granada, Spain}

@@

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} program will be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side would be installed in the corporate SOC. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the information flows labelled as `Info XX'. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras

@@

The use of a server is mainly based in the need of a powerful machine, able to work with massive amounts of data (\textit{Big Data}) \ref{BigData_11}. Thus, part of the high computational cost methods to apply will be derived to this high-performance server, as the mobile devices do not count with enough computational power. These methods will include Data Mining \cite{Cios07DataMining} and Machine Learning \ref{MachineLearning_Bishop06} techniques. This server will also centralise the data gathering from all the devices in the company, composing a big database to which the commented techniques will be applied.

@@

All data in MUSES will be encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
% Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)
